---
title: 'Assignement 1: Linear Regression'
author: "Bob Merkus, Tom Hartgers, Benine Karssen, Lucas Graas"
date: "12/2/2021"
output: html_document
---

1 Introduction
Hello

1.1 Dataset - Lucas
1.2 Research questions
1.3 Data exploration
1.3.1 Bivariate Relations
1.3.2 Variable distributions

**2 Simple Linear Regression**  

```{r}
out1 <- lm(clean_data$SWL_T ~ clean_data$Degree, data = clean_data)
```

**2.1 Coefficients - Benine**
**2.2 P-values - Benine**
**2.3 Confidence Interval (CI) - Tom** 
Compute the confidence intervals for the parameters of the model with a 95% confidence level.
```{r}
confint(out1)
```
None of the confidence intervals contain the value 0. Therefore we can be 95% sure that if we compute our analysis an infinite number of times, 95% of all confidence intervals will surround the true value of the parameters. Therefore we can reject the null hypothesis of our model. 

**2.4 Model fit - Tom** 

3 Multiple Linear Regression - Bob
3.1 Compare models (RMSE, AIC, BIC)
3.2 Interpret final model
3.3 Conclusions regarding model
3.3.1 Inference
3.3.2 Predictions 


```{r, warning = F}
source("data_import.R")


# plot game per age
p1 = clean_data %>% 
  ggplot() +
  geom_boxplot(aes(x = Age, y = Game))
p1
```